Clean and Process Raw Data

### 2020-05-19 data-raw/README.Rmd
clean up line breaks and fix warnings in R code

The raw data are located in the `data` folder of the installed
_rice.awd.pests_

@@

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

>>>>

The raw data are located in the `data` folder of the installed _rice.awd.shb_

@@

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- as.data.frame(as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))
